---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "70%"
)
```

# MusicScienceData

<!-- badges: start -->
<!-- badges: end -->

`MusicScienceData` is an R package that offers example datasets for suitable for exploration of basic analyses (correlation, comparison of means, etc.).

## Installation

The development version of this package can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tuomaseerola/MusicScienceData")
```
## Example

These are the first four rows of the `chords` dataset in the library:

```{r}
library(MusicScienceData)
d <- MusicScienceData::chords # Consonance ratings for 25 chords from Lahdelma & Eerola 2020
knitr::kable(d[1:4,])
# Are Consonance ratings dependent on Chord Size?
boxplot(rating ~ chord_size,data = d,col='lightblue')
```

## Datasets

Currently the following datasets are included:

| dataset             | Stim. N|Concepts                | Study                  |
| :------------------ | :----- |:-----------------------|
| chords              | 25     |Consonance ratings      | Lahdelma & Eerola 2020 |
| soundtracks         | 110    |Emotion ratings         | Eerola & Vuoskoski 2011|
| soundtracks_features| 110    |Acoustic features       | Related to soundtracks|
| sadness             | NA     | Attitude ratings towards sad music| Eerola & Peltola 2016  |
| annotations         | 100    | Annotations of 8 concepts | Unpublished data       |
| annotations_features| 100    | Acoustic features      | Unpublished        |

## Another example

Here is an example of the `sadness` dataset.
```{r}
knitr::kable(MusicScienceData::sadness[1:4,1:10])
```

We can look at the distribution of the ratings to one of the questions:

```{r MusicScienceData, echo = TRUE,warning=FALSE,message=FALSE}
library(ggplot2)
library(tidyverse)
MusicScienceData::sadness %>% 
  drop_na(ASM10) %>%
  ggplot(aes(x = ASM10))+
  geom_histogram(bins=7,fill="grey", colour='black')+
  scale_x_continuous(breaks = seq(1,7,by=1))+ 
  ggtitle('Listening to sad music induces unpleasant feelings in me')+
  ylab('Count')+
  xlab('1 = Strongly disagree, 7 = Strongly agree')+
  theme_bw()+
  theme(plot.title = element_text(size=12))
```

## Citation
Eerola, T. (2021). MusicScienceData. Open datasets for Music and Science Tutorials. https://github.com/tuomaseerola/MusicScienceData


## References

Lahdelma, I. & Eerola, T. (2020). Cultural familiarity and musical expertise impact the pleasantness of consonance/dissonance but not its perceived tension. _Scientific Reports(10), 8693_. [https://doi.org/10.1038/s41598-020-65615-8](https://doi.org/10.1038/s41598-020-65615-8)

Eerola, T. & Peltola, H.-R. (2016). Memorable Experiences with Sad Music - Reasons, Reactions and Mechanisms of Three Types of Experiences. _PlosOne, 11(6)_, e0157444. [http://dx.doi.org/10.1371/journal.pone.0157444](http://dx.doi.org/10.1371/journal.pone.0157444)

Eerola, T. & Vuoskoski, J. K. (2011). A comparison of the discrete and dimensional models of emotion in music. _Psychology of Music, 39(1)_, 18-49. [https://doi.org/10.1177/0305735610362821](https://doi.org/10.1177/0305735610362821)
